\documentclass[letterpaper]{article}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{epigraph}
\usepackage{lipsum}
\usepackage{hyperref}
\usepackage{tocloft}

\usepackage{setspace, amsmath}

\usepackage[centering,includeheadfoot,margin=2cm]{geometry}
\usepackage{xcolor}
\usepackage{calc,blindtext}

\renewcommand\epigraphflush{flushright}
\renewcommand\epigraphsize{\normalsize}
\setlength\epigraphwidth{0.6\textwidth}

\definecolor{titlepagecolor}{cmyk}{1,.60,0,.40}

\DeclareFixedFont{\titlefont}{T1}{ppl}{b}{it}{1.0in}

\makeatletter
\def\printauthor{%
    {\large \@author}}
\makeatother
\author{%
    Nico Taljaard \\
    10153285 \vspace{20pt} \\
    Gerhard Smit \\
    12282945 \vspace{20pt} \\
    Martin Schoeman \\
    10651994 \\
}

% The following code is borrowed from: http://tex.stackexchange.com/a/86310/10898

\newcommand\titlepagedecoration{%
	\begin{tikzpicture}[remember picture,overlay,shorten >= -10pt]
	
		\coordinate (aux1) at ([yshift=-15pt]current page.north east);
		\coordinate (aux2) at ([yshift=-410pt]current page.north east);
		\coordinate (aux3) at ([xshift=-4.5cm]current page.north east);
		\coordinate (aux4) at ([yshift=-150pt]current page.north east);
		
		\begin{scope}[titlepagecolor!40,line width=12pt,rounded corners=12pt]
			\draw
			  (aux1) -- coordinate (a)
			  ++(225:5) --
			  ++(-45:5.1) coordinate (b);
			\draw[shorten <= -10pt]
			  (aux3) --
			  (a) --
			  (aux1);
			\draw[opacity=0.6,titlepagecolor,shorten <= -10pt]
			  (b) --
			  ++(225:2.2) --
			  ++(-45:2.2);
		\end{scope}
			\draw[titlepagecolor,line width=8pt,rounded corners=8pt,shorten <= -10pt]
			  (aux4) --
			  ++(225:0.8) --
			  ++(-45:0.8);
		\begin{scope}[titlepagecolor!70,line width=6pt,rounded corners=8pt]
			\draw[shorten <= -10pt]
			  (aux2) --
			  ++(225:3) coordinate[pos=0.45] (c) --
			  ++(-45:3.1);
			\draw
			  (aux2) --
			  (c) --
			  ++(135:2.5) --
			  ++(45:2.5) --
			  ++(-45:2.5) coordinate[pos=0.3] (d);   
			\draw 
			  (d) -- +(45:1);
		\end{scope}
	\end{tikzpicture}
}

\begin{document}

\begin{titlepage}

\noindent
\titlefont Laminin \par
\epigraph{XGame - Derivco \\ Architecture requirements.}%
{\textit{ 23/05/2014 }\\ \textsc{ }}
\null\vfill
\vspace*{4cm}
\noindent
\hfill
\begin{minipage}{0.35\linewidth}
    \begin{flushright}
        \printauthor
    \end{flushright}
\end{minipage}
%
\begin{minipage}{0.02\linewidth}
    \rule{1pt}{125pt}
\end{minipage}
\titlepagedecoration
\end{titlepage}

% % % % % % % % % % % % % % %
% 							%
%	Remainder of document	%
% 							%
% % % % % % % % % % % % % % % 

	\newpage
		{\LARGE \bf Change Log}\\[2em]
		
		\begin{tabbing}
			\hspace*{2.5cm}\=\hspace*{2.5cm}\=\hspace*{8cm}\=\hspace*{3cm} \kill
			17/05/2014	\> Version 1.0	\> Document Created 							\> Nico Taljaard \\
			17/05/2014	\> Version 1.0	\> Access channel \& Quality requirements		\> Nico Taljaard \\
			18/05/2014	\> Version 1.0	\> Integration requirements, Architectural constraints \\
						\>				\>	\& added quality requirements 				\> Nico Taljaard \\
		\end{tabbing}
		
	\newpage
		\renewcommand\contentsname{TABLE OF CONTENTS}
		\newcommand\contentsnameLC{\colorbox{blue}{\makebox[\textwidth-2\fboxsep][l]{\bfseries\color{white} Table of Contents}}}
		
		\renewcommand{\cftdot}{}
		\hypersetup{linktocpage}
		\tableofcontents
		
		\begin{flushleft}
			\LARGE\href{https://github.com/njTaljaard/Laminin_CorpseSlasher/}{Git repository: Laminin - Corpse Slasher}
		\end{flushleft}
		
	\newpage
		
		\section*{\colorbox{blue}{\makebox[\textwidth-2\fboxsep][l]{\bfseries\color{white} Access channel requirements }}} \addcontentsline{toc}{section}{Access channel requirements}
		\vspace{0.1in}
		
		The system will be accessible by human users through the following channels:
		\begin{itemize}
			\item From a desktop application running on any Windows/Linux operating system.
			\item From a mobile device running Android application clients.
		\end{itemize}
		
		\vspace{0.2in}
		\section*{\colorbox{blue}{\makebox[\textwidth-2\fboxsep][l]{\bfseries\color{white} Quality requirements}}} \addcontentsline{toc}{section}{Quality requirements}
		\vspace{0.1in}
		
			The quality requirements are the requirements around the quality attributes of the systems and the
			services it provides.
			
			\subsection*{Performance}
			\addcontentsline{toc}{subsection}{Performance}
			\vspace{0.1in}
			
			\begin{enumerate}
				\item Desktop \& Mobile application:
					\begin{itemize}
						\item Should not go under a playable frames rate of 60.
						\item Should not have high data transfers for sending \& receiving information.
						\item Should not require more the 4 logical processing cores.
					\end{itemize}
			
				\item Desktop application:
					\begin{itemize}
						\item Should not use more the 3GB of system memory.
					\end{itemize}
			
				\item Mobile application:
					\begin{itemize}
						\item Should not use more the 2GB of system memory.
						\item Should not use access battery usage.
					\end{itemize}
					
				\item Backend server:
					\begin{itemize}
						\item Should be able to handle at least 100 connections.
						\item Should not use more then 10GB of system memory to handle connections.
						\item Database updates should be complete within a 1 second time frame.
						\item Database requests should be complete within 5 second time frame.
					\end{itemize}
			\end{enumerate}
			
			\subsection*{Reliability}
			\addcontentsline{toc}{subsection}{Reliability}
			\vspace{0.1in}
			
			\begin{enumerate}
				\item Desktop \& Mobile:
					\begin{itemize}
						\item Client should be able to recover from a crash within 30 seconds.
						\item Retry opening connection within 5 seconds if connection loss.
						\item Reload assets if data is lost.
					\end{itemize}
				\item Backend Server:
					\begin{itemize}
						\item Should provide 99\% connection availability.
						\item Should provide 99\% OAuth login availability.
						\item Should not crash due to over welling client connections.
						\item Should not crash due to undefined incoming data.
					\end{itemize}
			\end{enumerate}
			
			\subsection*{Scalability}
			\addcontentsline{toc}{subsection}{Scalability}
			\vspace{0.1in}
			
			\begin{enumerate}
				\item The server should be able to add multiple servers to handle clients.
				\item The server should scale to any amount of client connections.
			\end{enumerate}
			
			\subsection*{Security}
			\addcontentsline{toc}{subsection}{Security}
			\vspace{0.1in}
			
			General security conditions.
			\begin{enumerate}
				\item Use OAuth LDAP for connection through social media e.g. Facebook, Twitter, Google+.
				\item Clean up all incoming data on client and server for incorrect formats, data types \& lengths.
				\item Test if the incoming data comes from authenticated user.
				\item Local authentication users needs secure connection for login and password retrieval.
			\end{enumerate}
			
			\subsection*{Maintainability}
			\addcontentsline{toc}{subsection}{Maintainability}
			\vspace{0.1in}
			
			\begin{enumerate}
				\item Database off site backups should be creatable.
				\item Desktop \& mobile application should be update able with further maps.
			\end{enumerate}
			
			\vspace{0.2in}
			\section*{\colorbox{blue}{\makebox[\textwidth-2\fboxsep][l]{\bfseries\color{white} Integration requirements}}} \addcontentsline{toc}{section}{Integration requirements}
			\vspace{0.1in}
			
			\subsection*{Integration channels}
			\addcontentsline{toc}{subsection}{Integration channels}
			\vspace{0.1in}
			
			This system will be able to access:
			\begin{enumerate}
				\item A local MySQL datbase to access player information \& leader board.
				\item External social media LDAP servers for players who would like to share their achievements.
				\item External application connection to the server should only be encrypted during login.
			\end{enumerate}
		
			\vspace{0.2in}
			\subsection*{Protocols}
			\addcontentsline{toc}{subsection}{Protocols}
			\vspace{0.1in}
		
			This system will use the following protocols:
			\begin{enumerate}
				\item Java client server for communication between the Desktop \& Mobile application and the backend server. 
				\item JSON is used for the data encoding 
				\item LDAP protocol is used by the LDAP adapter to communicate with the LDAP database.
				\item SQL to communicate with the relational datebase.
			\end{enumerate}
		
			\vspace{0.2in}
			\subsection*{API specification}
			\addcontentsline{toc}{subsection}{API specification}
			\vspace{0.1in}
		
		
		
		\vspace{0.2in}
		
		
		\section*{\colorbox{blue}{\makebox[\textwidth-2\fboxsep][l]{\bfseries\color{white} Architectural constraints}}} \addcontentsline{toc}{section}{Architectural constraints}
		\vspace{0.1in}
		
			\subsection*{Technologies}
			\addcontentsline{toc}{subsection}{Technologies}
			\vspace{0.1in}
			
				\begin{enumerate}					
					\item \textbf{Graphics}
					\\OpenGL 3.0 - 4.4 will be used as the rendering language within the game engine.
					
					\item \textbf{Audio}
					\\OpenAL will be used for audio within the game.
					
					\item \textbf{Development language}
					\\The desktop \& mobile application as well as the server will be implemented using JavaSE.
					
					\item \textbf{LDAP integration}
					\\SocialAuth is a Java implemented OAuth library that will be the used to communicate with external LDAP servers.
					
					\item \textbf{Networking}
					\\jSpiderMonkey will be used to handle client side networking within the jMonkeyEngine framework.
					
					\item \textbf{Persistence}
					\\MySQL will be used to store all data which is accessible through a JDBC connection.
				\end{enumerate}
				
			\subsection*{Architectural patterns/frameworks}
			\addcontentsline{toc}{subsection}{Architectural patterns/frameworks}
			\vspace{0.1in}
			
				\begin{enumerate}
					\item \textbf{Game Engine}
					\\jMonkeyEngine 3.0 is a Java Framework that will be used to implement the game.
					
					\item \textbf{Client Server}
					\\A client server pattern should be used between the external application and the backend server.
					
					\item \textbf{Layering}
					\\The backend server should implement layering from connections to clients down to the LDAP and MySQL server connections.
				\end{enumerate}
			
		\vspace{0.2in}
		
\end{document}